A multinomial spatio-temporal model for sexual risk behaviour with application to adolescent girls and young women in 13 sub-Saharan African countries

### 2022-01-03 src/docs_04-01-22-update/04-01-22-update.Rmd
Update slides for tomorrow #50

@@

@@

## References {.allowframebreaks}

>>>>

\begin{table}
\centering
\begin{tabularx}{\textwidth}{lXlX}
\toprule
Category & Description & Risk ratio & Notes \\ 
 \midrule
None & Not sexually active & 0 & Ignores incidence from e.g. drug injection (assumed to be negligible). \\
Low & One cohabiting sexual partner & 1 & Baseline category. \\
High & Non-regular sexual partner(s) & 1.72 & From ALPHA network pooled analysis. Supported by Jia et al. \\
Very high & Young women from key populations & 13 & Sabin et al. \\
\bottomrule
\end{tabularx}
\caption{HIV risk categories and risk ratios.}
\label{tab:risk-categories}
\end{table}

```{r echo=FALSE}
knitr::include_graphics("depends/category-flowchart.pdf")
```

@@

Final model selected:

\begin{align}
    y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\
    \log(\lambda_{itak}) &= \beta_k + \alpha_{ak} + \phi_{ik} + \gamma_{tk} + \theta_{iat}.
\end{align}

## Benefits of smoothing

1. Get estimates even where there isn't direct data

* Some people think of this as "making up data"
* In some sense all estimates are "made up" though
* Uncertainty should be higher in regions with infilling
* Perhaps we do a bad job communicating uncertainty, or it's just hard

## Benefits of smoothing

2. Borrow information across space, surveys, categories

* Space-category effects, survey-category effects, space-survey-category effects (using Kronecker products)
* Fun to think about what models might be reasonable for this and whether structured category effects might be interesting
  * e.g. some model for misclassification of individuals into categories could give a kind of structured category effect (currently it's IID always)
* Wonder to what extent we're oversmoothing
  * e.g. might expect to see discontunities in the data (e.g. urban centers) which we're smoothing away

@@
